Verification of OpenSSL's SHA3 \keccak\ function using the Software Analysis Workbench

### 2022-01-06 paper/related.tex
Revises related.tex

Our work built upon the SHA2-256 inner hash function verification (!--Citation1--).
Citation1 expanded the methodology by which Amazon's s2n HMAC was verified (!--Citation2--).
Both compared equivalent C and Cryptol specification through SAW.
While SHA3 is not implemented in s2n, Citation2 utilized both a high-level and low-level cryptol specification, similar to our work.
Citation1's verification of OpenSSL's SHA2-256 implementation served as a direct predecessor to our work.
While SHA2 is also part of NIST's Secure Hash Algorithms, it's internal structure differs vastly from the more complex and resistant SHA3.

>>>>

The verification of OpenSSL's SHA2-256 implementation served as a direct predecessor to this work (!Citation2).
While SHA2 is also part of NIST's Secure Hash Algorithms, its internal structure differs vastly from the more complex and resistant SHA3.
The SHA2 proof, in turn, expanded the methodology by which Amazon's s2n HMAC was verified (!Citation2).
While SHA3 is not implemented in s2n, the HMAC verification utilized both a high-level and low-level cryptol specification in a similar manner to this work.
Both prior works compared equivalent C and Cryptol specification through SAW.
